Changing Dynamics of Urban Bike Thefts: Understanding Trends to Inform Future Prevention Efforts

### 2024-12-03 paper/paper.qmd
Update some detail of this paper.
This update include the README file, reference.bib also some details in the paper.

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Jin Zhang
thanks: "Code and data are available at: https://github.com/KrystalJin1/Toronto_Bike_Theft_Analysis.git "
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

library(tidyverse)
library(rstanarm)
library(knitr)
library(kableExtra)
library(modelsummary)
library(here)
library(readr)
library(arrow)
library(bayesplot)
library(ggplot2)
library(styler)
```

@@

# Data {#sec-data}
We used the R programming language [@citeR] to analyze the data and plot the graphs for this paper. The folder structure for this paper follows the starter folder created by [@rohan]. I also referenced many of the examples and techniques provided by Telling Stories with Data [@alexander2023telling], which helped me understand how to visualize the data and communicate the findings effectively. In addition, the `tidyverse` [@citetidyverse] packages are essential for simplifying data cleaning and analysis.`styler` [@citestyler] is used in arranging code style. I also plotted the graphs with `ggplot2` [@citeggplot2] and read the CSV file with `here` [@citehere]. We used the `knitr` [@citeknitr] to show the table.The `rstanarm` package [@citerstanarm] allowed us to fit Bayesian regression models using Hamiltonian Monte Carlo. For improving the appearance and functionality of our tables, we employed the `kableExtra` package [@citekableExtra]. Data import and processing were facilitated by the `readr` package [@citereadr] for fast and efficient reading of tabular data, and the `arrow` package [@citearrow] for reading and writing data in various formats including Parquet. The `modelsummary` package [@citemodelsummary] provided tools to summarize and present regression model outputs in a convenient and customizable way. Visualizations of Bayesian models were created using the `bayesplot` package [@citebayesplot] and `styler` [@citestyler] used in arranging code style.

@@

>>>>

---
title: "Changing Dynamics of Urban Bike Thefts: Understanding Trends to Inform Future Prevention Efforts"
subtitle: "A Replication Quantitative Analysis Using Toronto Police Data (2014-2024)"
author: 
  - Jin Zhang
thanks: "Code and data are available at: https://github.com/KrystalJin1/Toronto_Bike_Theft_Analysis.git "
date: today
date-format: long
abstract: "This study utilizes a decade of Toronto Police Service data spanning from 2014 to 2024 to examine the dynamics of bicycle thefts, focusing specifically on monthly and hourly variations, as well as the influence of different locations. Analysis reveals that the theft rates are higher in summer months and during late evening hours under the apartment buildings. This research highlights critical insights into urban crime patterns, providing valuable information for enhancing security measures and planning urban safety strategies effectively."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

library(tidyverse)
library(rstanarm)
library(knitr)
library(kableExtra)
library(modelsummary)
library(here)
library(readr)
library(arrow)
library(bayesplot)
library(ggplot2)
library(styler)
library(plumber)
```

@@

# Data {#sec-data}
We used the R programming language [@citeR] to analyze the data and plot the graphs for this paper. The folder structure for this paper follows the starter folder created by [@rohan]. I also referenced many of the examples and techniques provided by Telling Stories with Data [@alexander2023telling], which helped me understand how to visualize the data and communicate the findings effectively. In addition, the `tidyverse` [@citetidyverse] packages are essential for simplifying data cleaning and analysis.`styler` [@citestyler] is used in arranging code style. I also plotted the graphs with `ggplot2` [@citeggplot2] and read the CSV file with `here` [@citehere]. We used the `knitr` [@citeknitr] to show the table.The `rstanarm` package [@citerstanarm] allowed us to fit Bayesian regression models using Hamiltonian Monte Carlo. For improving the appearance and functionality of our tables, we employed the `kableExtra` package [@citekableExtra]. Data import and processing were facilitated by the `readr` package [@citereadr] for fast and efficient reading of tabular data, and the `arrow` package [@citearrow] for reading and writing data in various formats including Parquet. The `modelsummary` package [@citemodelsummary] provided tools to summarize and present regression model outputs in a convenient and customizable way. Visualizations of Bayesian models were created using the `bayesplot` package [@citebayesplot] and `styler` [@citestyler] used in arranging code style.We also use the `plumber` [@citeplumber] to build the API.

@@

### API for Predictive Analysis
In addition to the statistical methods applied in our study, we utilized a specifically developed API to predict bike theft incidents based on several variables including the hour of the day, month of the year, premises type, and the cost of the bike. This API, built using the `plumber` and `rstanarm` packages, leverages a Bayesian logistic regression model trained on historical data from 2014 to 2024, as sourced from the Toronto Police Service. The API's predictive functionality allows us to dynamically assess the risk of bike theft by integrating real-time data inputs, offering a practical application for our research findings.

The API processes input variables such as the occurrence hour and month, type of premises, and bike cost to estimate the probability of a theft. This is done by calculating the odds of theft using the model's posterior samples for each input factor. The resulting predictions provide insights into the patterns of theft across different times and locations, demonstrating how these factors influence bike theft risk. This predictive tool not only validates our analytical models but also serves as a bridge between theoretical research and practical, real-world application, enhancing the utility of our findings for urban safety and crime prevention strategies.
